-- GeneCan----
Author: Sam Herr, Krista Miller, Dan Pollard
Description: This markdown prepares files for use in GeneCan which find Candidate genes in
            QTL location found by QTLseqR packages. The input of these files are .vcf                    files.
            
Email: Samuelkherr@gmail.com for any questions
-------------------------

```{r load packages} 

###Adapted from Kuo et. al. - Full RNA/Protein analysis for Kuo et al: A simple mass-action model predicts protein timecourses from mRNA trajectories during a dynamic response in S. cerevisiae

library("QTLseqr")
library("tidyverse")
library("gtools")
library(jsonlite)
library(openxlsx)


packages = c('QTLseqr', "tidyverse", "gtools", "jsonlite", "openxlsx")
 
## Now load or install&load all
 package.check <- lapply(
   packages,
   FUN = function(x) {
     if (!require(x, character.only = TRUE)) {
       install.packages(x, dependencies = TRUE)
       library(x, character.only = TRUE)
     }
  }
 )
```


Run Qtlseqr on autofluorence and gene of interests (GOIs) 
Get initial estimates of GOI dsNP and autofluorescence dSNP
Input file directories and  timepoints of interest

```{r}

source("R/dSNP-functions")
source("R/GeneCan-functions")
################File INPUT#############################################################
##Place all timepoints in AF experiment
times <- list("t0", "t2", "t5","t8")
##The folder containing gene of interests vcf files.
allGOI <- ListFiles("GOIs")
##Have autofluoresence vcf tables in a folder
allAf <- ListFiles("AutoF")

##########################################################################################


##Get initial GOI and Autofluorescence
imputatedAuto <- getImputation(allGOI, allAf, times)
##outputs normalized deltaSNPS for each gene and timepoint nested in their respective timepoint 
dSNPS <- lapply(times, getTime, GOI = allGOI, AF = imputatedAuto)

###Builds a single list containing all experimental data
##For use in GeneCan and plotting
len = length(dSNPS)
alldSNP <- list()
for( i in 1:len) {
  alldSNP <- c(alldSNP,dSNPS[[i]])
  
} 
alldSNP <- lapply(alldSNP,limitIt)
alldSNP<- alldSNP[allGOI]


###List use for QTL hotspots
normSigR <- lapply(alldSNP,getQTLTables) 

```


GeneCan will output excel files for each Gene and timepoint.
GeneCan finds the Genes associated with each QTL region gotten from the list normSigR
For each gene it gives the average dSNP score and then phenotype and Go terms associated with the main gene of interest (in our case FIG1)
It also compares interactors and regulators in common with main gene of interest (FIG1)

```{r}
####Code for GeneCAN to run
###MAKE SURE TO LOOK AT the function autoQTLsnps for gene names
genes <- "gff_final_clean.txt"

GOIname <- names(alldSNP)

####To edit phenotype/GO term list and comparative Gene go into the Genecan-function itself on line 393.
GeneCan <- lapply(GOIname, autoQTLsnps, alldSNP, genes, normSigR)
```

